\chosentitle

### 2024-10-22 paper/main.tex
comments til p12

\section{Methods}\label{sec:methods}

@@

The final product of the \harps\ data reduction pipeline is a one-dimensional unrectified spectrum, resampled onto a single wavelength array where all echelle orders have been stitched together. Because we are interested in fitting the continuum on a per-order basis, we instead use the \texttt{e2ds} data products. These are extracted one-dimensional unrectified spectra of each echelle order, with the wavelength solution represented by a low order polynomial. In early experiments we fit the spectra in the \texttt{e2ds} data products directly, an example of which can be seen in Figure~\ref{fig:harps-alf-cen-a}. However, for some exposures we noticed systematic residuals that could be explained by a 2D artefact in the image plane (e.g., a ghost or reflection). While we expect that flat-fielding should have already removed these kinds of artefacts, it did prompt us to explore using the nightly blaze calibration files. Using the calibration blaze files mitigated much of the visible structure, and expectedly provided spectra with a simpler, flatter shape. For these reasons, in all experiments except for the one shown in Figure~\ref{fig:harps-alf-cen-a}, we chose to fit blaze-corrected echelle orders.\\

@@

\begin{figure*}
    \includegraphics[width=\textwidth, height=\textwidth]{../code/harps_examples.pdf}
    \caption{Continuum-rectified \harps\ spectra of example spectral types from B to M. The model used here includes 16 basis vectors for stellar absorption, and 4 basis vectors for telluric transmission. \todo{Only BAF-type stars used blaze-corrected spectra. Need to download blazes for others and re-run.}\label{fig:harps-examples}}
\end{figure*}

@@

The first defined experiment involves fitting stars of a variety of spectral types. The rectified spectra for selected example stars in this experiment are shown in Figure~\ref{fig:harps-examples}, where stars are ordered and coloured by their spectral type listed in \project{SIMBAD}. From these rectified spectra it is clear that the model performs well on a variety of stellar types and evolutionary stages. HD 45418, a B4-type star, is the hottest star in our sample  \citep[$T_\mathrm{eff} = 16{,}750\,K$ according to ][]{2015MNRAS.454...28M}, and far exceeds the upper temperature bound (8,000\,K) of the synthetic grid that we factorized using NMF. The fit to HD 45418 is quite good, despite this star being well outside the model grid. All other example stars shown in Figure~\ref{fig:harps-examples} have literature stellar parameters that place them well within the bounds of the factorized model grid. Most stars observed with \eso/\harps\ are predictably on the main-sequence, since they are more frequently subject to radial velocity exoplanet searches than evolved stars. HD 203050 (K2) is the only red giant branch in our sample. This is not obvious from Figure~\ref{fig:harps-examples}, suggesting the model does just as well on red giant branch stars as it does on main-sequence stars. This has been our experience in other works using this method on SDSS-V optical and near-infrared spectra (Casey et al., in prep).\\

>>>>

\section{Methods}\label{sec:methods}
\ajw{Weinberg does a thing where he has a table of every variable and what it is at the beginning of the methods.  It makes things much easier to skim, and I think it would work well here.}

@@

The final product of the \harps\ data reduction pipeline is a one-dimensional unrectified spectrum, resampled onto a single wavelength array where all echelle orders have been stitched together. Because we are interested in fitting the continuum on a per-order basis, we instead use the \texttt{e2ds} data products. These are extracted one-dimensional unrectified spectra of each echelle order, with the wavelength solution represented by a low order polynomial. In early experiments we fit the spectra in the \texttt{e2ds} data products directly, an example of which can be seen in Figure~\ref{fig:harps-alf-cen-a}. However, for some exposures we noticed systematic residuals that could be explained by a 2D artefact in the image plane (e.g., a ghost or reflection). While we expect that flat-fielding should have already removed these kinds of artefacts, it did prompt us to explore using the nightly blaze calibration files. Using the calibration blaze files mitigated much of the visible structure, and expectedly \ajw{``as expected'', maybe} provided spectra with a simpler, flatter shape. For these reasons, in all experiments except for the one shown in Figure~\ref{fig:harps-alf-cen-a}, we chose to fit blaze-corrected echelle orders.\\

@@

\begin{figure*}
    \includegraphics[width=\textwidth, height=\textwidth]{../code/harps_examples.pdf}
    \caption{Continuum-rectified \harps\ spectra of example spectral types from B to M. The model used here includes 16 basis vectors for stellar absorption, and 4 basis vectors for telluric transmission. \todo{Only BAF-type stars used blaze-corrected spectra. Need to download blazes for others and re-run.} \ajw{consider a lower line weight} \ajw{I feel like i'm being thick but I don't get whey these ever go above 1. Also, are you sure that the clam continuum is where the theoretical continuum is the the M1 star?}}\label{fig:harps-examples}}
\end{figure*}

@@

The first defined experiment involves fitting stars of a variety of spectral types. The rectified spectra for selected example stars in this experiment are shown in Figure~\ref{fig:harps-examples}, where stars are ordered and coloured by their spectral type listed in \project{SIMBAD}. From these rectified spectra it is clear that the model performs well on a variety of stellar types and evolutionary stages. HD 45418, a B4-type star, is the hottest star in our sample  \citep[$T_\mathrm{eff} = 16{,}750\,K$ according to ][]{2015MNRAS.454...28M}, and far exceeds the upper temperature bound (8,000\,K) of the synthetic grid that we factorized using NMF. The fit to HD 45418 is quite good, despite this star being well outside the model grid. All other example stars shown in Figure~\ref{fig:harps-examples} have literature stellar parameters that place them well within the bounds of the factorized model grid. Most stars observed with \eso/\harps\ are predictably \ajw{drop ``predictably'' maybe} on the main-sequence, since they are more frequently subject to radial velocity exoplanet searches than evolved stars. HD 203050 (K2) is the only red giant branch in our sample. This is not obvious from Figure~\ref{fig:harps-examples}, suggesting the model does just as well on red giant branch stars as it does on main-sequence stars. This has been our experience in other works using this method on SDSS-V optical and near-infrared spectra (Casey et al., in prep).\\
